---
title: "Step 2: Descriptive Codes"
page-layout: full
reference-location: margin
citation-location: margin
bibliography: ref-1.bib
execute: 
  echo: false
---

```{r}
#| include: false

library(readxl)
library(DT)
library(tidyverse)

studentA <- read_xlsx(
  here::here("data", "code_book.xlsx"), 
  sheet = "studentA"
  )

studentB <- read_xlsx(
  here::here("data", "code_book.xlsx"), 
  sheet = "studentB"
  )
```

The second step in the qualitative analysis is creating qualitative codes for each unit of analysis (UOA).

The process of coding in qualitative research, where a researcher makes notes next to each UOA that are potentially relevant to addressing the research question. Codes act as labels, assigning "symbolic meaning" to each UOA [@miles]. In our context, each line of R code is a UOA, which is why we are "coding code."

The initial qualitative codes assigned to the units of analysis can be thought of as the "first cycle codes." There are over 25 different methods for creating first cycle codes, each with a particular focus and purpose. In our paper, we discuss two specific methods of coding we believe are most relevant to investigating computing code: descriptive coding and in vivo coding.

For this research, I chose to use descriptive codes as I sought to *describe* the computing skills students were using in their research project. With in vivo coding, these descriptions would be required to take on the voice (code) of each student, which I felt constrained the possible descriptions available to me.

----

## Student A -- Descriptive Codes

If you are interested in seeing the original R script file from Student A, 
you can find that [here](data/studentA_code.qmd). If while reading you
wonder what the output of a specific statement is, I have reproduced Student
A's code using the `penguins` dataset [@penguins], available
[here](data/studentA_reproduced.qmd). 

```{r}
#| echo: false

studentA %>% 
  select(code, descriptive_code) %>% 
  datatable(class = 'row-border stripe', 
            colnames = c("R Code", "Descriptive Code")
            )


```


## Student B -- Descriptive Codes

If you are interested in seeing the original R script file from Student A, 
you can find that [here](data/studentB_code.qmd). 


```{r}
#| echo: false

studentB %>% 
  select(code, descriptive_code) %>% 
  datatable(class = 'row-border stripe', 
            colnames = c("R Code", "Descriptive Code")
            )


```