---
title: "Reproducing Student A's Code"
page-layout: full
format: html
reference-location: margin
citation-location: margin
editor: visual
bibliography: ref.bib
execute: 
  error: true
---

The following analysis reproduces Student A's code in the context of the `penguins` dataset from the **palmerpenguins** package [@penguins].

```{r}
#| message: false

library(palmerpenguins)
library(tidyverse)

set.seed(123)
```

The only variable type missing from the `penguins` dataset is a variable similar to Student A's "Age" variable. The `pengins` dataset contains information on adult penguins. Depending on the size of the penguin, they can take between three and eight years until they begin breeding. Most species of penguins take at least five years. Thus, when creating an `age` variable in the `penguins` dataset I simulated values from a Normal distribution with mean 5 and standard deviation 1.

```{r}
penguins <- penguins |> 
  mutate(age = rnorm(n = nrow(penguins), mean = 5, sd = 1), 
         age = round(age, digits = 0)
         )
```

## Reproducing Student A's Code

```{r}
#| eval: false

#upper anterior measurement Linear model
linearAnterior <- lm(penguins$bill_length_mm~penguins$bill_depth_mm)
summary(linearAnterior)
linearAnterior
with(penguins, plot(bill_length_mm~bill_depth_mm,las = 1,col = ifelse(penguins$body_mass_g< 4050,"red","black")))
abline(linearAnterior)
plot(linearAnterior)


#Exponential function
expAnterior <- lm(penguins$bill_length_mm~log(penguins$bill_depth_mm))
summary (expAnterior)
expAnterior
with(penguins, plot(bill_length_mm~log(bill_depth_mm), las = 1, col = ifelse(penguins$body_mass_g< 4050,"red","black")))
abline(expAnterior)
plot(expAnterior)
summary(expAnterior)


early <- subset(penguins, year<2007)
mid <- subset(penguins, year<2009 & year>2007)
penguinsSub <- transform(penguins, Age = as.integer(age))
Early <- subset(penguinsSub, year<2008)
Mid <- subset(penguinsSub, year<2009 & year>2007)
EarlyWeightAge <- ddply(Early, ~Age, summarise, meanWE=mean(body_mass_g, na.rm = T))
EarlyLengthAge <- ddply(Early, ~Age, summarise, meanLE=mean(bill_length_mm, na.rm = T))
MidLengthAge <- ddply(Mid, ~Age, summarise, meanLM=mean(bill_length_mm, na.rm = T))
WeightChange <- rep(NA, 9)

library(plyr)
WeightAge <- ddply(penguinsSub, ~Age, summarise, meanW=mean(body_mass_g, na.rm = T))
LengthAge <- ddply(penguinsSub, ~Age, summarise, meanL=mean(bill_length_mm, na.rm = T))
plot(EarlyLengthAge$meanLE~EarlyLengthAge$Age,las = 1,ylab = "Fork Length (mm)",xlab = "Age")
lines(EarlyLengthAge$meanLE~EarlyLengthAge$Age)
points(MidLengthAge$meanLM~MidLengthAge$Age,col = "red")
lines(MidLengthAge$meanLM~MidLengthAge$Age,col = "red")
legend(6, 48, legend = c("1998-2003", "2006-2017"),col = c("black", "red"), lty = 1:1,cex = 0.8)

#Tanner's code/help
WeightChange <- rep(NA, 9)
library(plyr)
WeightAge <- ddply(penguinsSub, ~Age, summarise, meanW=mean(body_mass_g, na.rm = T))
LengthAge <- ddply(penguinsSub, ~Age, summarise, meanL=mean(bill_length_mm, na.rm = T))
plot(WeightAge$meanW~WeightAge$Age)
plot(LengthAge$mean~LengthAge$Age)
WeightChange

Weight1 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==2], na.rm=TRUE)
Weight1
Length1 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==2], na.rm=TRUE)
Weight2 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==3], na.rm=TRUE)
Length2 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==3], na.rm=TRUE)
Weight3 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==4], na.rm=TRUE)
Length3 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==4], na.rm=TRUE)
Weight4 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==5], na.rm=TRUE)
Length4 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==5], na.rm=TRUE)
Weight5 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==6], na.rm=TRUE)
Length5 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==6], na.rm=TRUE)
Weight6 <- mean(penguinsSub$body_mass_g[penguinsSub$Age==7], na.rm=TRUE)
Length6 <- mean(penguinsSub$bill_length_mm[penguinsSub$Age==7], na.rm=TRUE)
# Weight7 - Length9 removed
x <- data.frame("Age" = 1:7, "Growth" = Weight1,Weight2,Weight3,Weight4,Weight5,Weight6)



```
