---
format: 
  revealjs:
    slide-number: false
    height: 900
    width: 1600
    logo: "images/cp_hex_logo.png"
    footer: "[USCOTS Quarto Workshop](https://atheobold.github.io/uscots-quarto/)"
    theme: [dark, styles.scss]
    embed-resources: true
editor: source
---

##  {background-image="images/05-style-crop.png" background-position="center" background-size="cover"}

::: {style="font-size: 6em; color: #FFFFFF;"}
Styling Quarto Presentations
:::

```{r}
#| label: set-up

library(tidyverse)
```


## Themes!

::: columns
::: {.column width="40%"}
[There are 11 built-in themes provided for Reveal presentations! The `default` and `dark` themes use fairly classic typography and color schemes and are a good place to start.]{.midi}

</br>

[The `default` theme is used automatically — use the theme option to switch to an alternate theme.]{.midi}
:::

::: {.column width="5%"}
:::

::: {.column width="55%"}

::: fragment
::: {.large}

```yaml
---
title: "Presentation"
format:
  revealjs: 
    theme: dark
---
```
:::

</br>
</br>

[Link to default themes available](https://quarto.org/docs/presentations/revealjs/themes.html#using-themes)
:::
:::
:::


# Incrementing

## Lists

::: columns
::: {.column width="45%"}

[**Locally**]{style="font-size: 1.25em; color: #ed8402;"}

```markdown
::: {.incremental}

- item 1
- item 2
- item 3

:::
```

</br>

::: {.incremental}

- item 1
- item 2
- item 3

:::
:::

::: {.column width="5%"}
:::

::: {.column width="45%"}
::: fragment
[**Globally**]{style="font-size: 1.25em; color: #ed8402;"}

```yaml
format:
  revealjs:
    incremental: true  
```
:::
:::
:::

## Pauses

If you don't have a list of things, but you want to increment components of your slide...

</br>

::: {style="font-size: 1.5em;"}

```markdown
content before the pause

. . .

content after the pause
```
:::

</br>

. . .

content before the pause

. . .

content after the pause

## Fragments

If you have columns and you would like to increment when and how columns appear...

</br>

::: columns
::: {.column width="30%"}
::: {.fragment .fade-in-then-out}
Fade out
:::
:::

::: {.column width="3%"}
:::

::: {.column width="30%"}
::: {.fragment .fade-in}
::: {.fragment .grow}
::: {.fragment .semi-fade-out}
Fade in then GROW then fade semi out
:::
:::
:::
:::

::: {.column width="3%"}
:::

::: {.column width="30%"}
::: {.fragment .fade-up}
Slide up while fading in
:::
:::
:::


## Implementation

::: {style="font-size: 1.5em;"}

```markdown
::: columns
::: {.column width="30%"}
::: {.fragment .fade-in-then-out}
Fade out
:::
:::

::: {.column width="3%"}
:::

::: {.column width="30%"}
::: {.fragment .fade-in}
::: {.fragment .grow}
::: {.fragment .semi-fade-out}
Fade in then GROW then fade semi out
:::
:::
:::
:::

::: {.column width="3%"}
:::

::: {.column width="30%"}
::: {.fragment .fade-up}
Slide up while fading in
:::
:::
:::
```
:::

</br>

[Learn more about fragments here!](https://quarto.org/docs/presentations/revealjs/advanced.html#fragments)

## Callouts 

If you want to remind your audience of something important...

</br> 

::: {style="font-size: 1.5em;"}
::: {.callout-tip}
# Same format!

Remember, you can use the same format to get a callout in a presentation!

```markdown
::: {.callout-tip}

:::
```
:::
:::

## Tabsets 

are quite useful for displaying content side-by-side...

</br>

::: panel-tabset
### `str_to_lower()`

converts all letters in the strings to lowercase

<br>

::: {style="font-size: 1.5em;"}
```{r}
#| echo: true
#| code-line-numbers: false
my_vector <- c("Hello,", "my name is", "Bond", "James Bond")
str_to_lower(my_vector)
```
:::

### `str_to_upper()`

converts all letters in the strings to uppercase

</br>

::: {style="font-size: 1.5em;"}

```{r}
#| echo: true
#| code-line-numbers: false

str_to_upper(my_vector)
```
:::

### `str_to_title()`

converts the first letter of the strings to uppercase

</br>

::: {style="font-size: 1.5em;"}
```{r}
#| echo: true
#| code-line-numbers: false
str_to_title(my_vector)
```
:::
:::

. . .

</br>

[Learn more about tabsets here!](https://quarto.org/docs/presentations/revealjs/#tabsets)

## Code Output

[Learn more about code output locations here!](https://quarto.org/docs/presentations/revealjs/#output-location)
